The fifteen year struggle of decentralizing privacy-enhancing technology

### 2014-04-03 paper.tex
Improved the text in chapter 5.11, to be more consistent

\section{Decentralized privacy-enhancing systems}
	\label{sec:decentralized}

@@

	\subsection{Comparison}
		In this subsection we will make a comparison between these networks, as seen in table \ref{tbl:comparison}. For each network, we will explain the following features:

		\begin{itemize}
			\item{Compatibility with Tor:} If the network is compatible with Tor, the network or some features of the network could be used for the decentralization of Tor.
			\item{Public implementation:} For each network we will explain whether a public implementation is available.
			\item{Used in practice:} Is the network used in practice?
			\item{Attack resistance:} We will explain the various weaknesses and possible attacks of each network.
			\item{Unlinkability:} Does the network hide the identities of the sender and/or receiver?
		\end{itemize}

>>>>

\section{Decentralized \mbox{privacy-enhancing} systems}
	\label{sec:decentralized}

@@

	\subsection{Comparison}
		Using the properties of each of the previously described networks, we can now draw a comparison between these networks. This is done in the form of a tabular overview, see table \ref{tbl:comparison}. The networks are compared according to the following features:

		\begin{itemize}
			\item{Compatibility with Tor:} Is the network compatible with Tor? Could the network or some features of the network be used for the decentralization of Tor?
			\item{Public implementation:} Does a publicly available implementation exist?
			\item{Used in practice:} Is the network used in practice?
			\item{Attack resistance:} What weaknesses does the network have and which attacks are possible?
			\item{Unlinkability:} Does the network hide the identities of the sender and/or receiver?
		\end{itemize}
